### 2012-03-26 exam4/2.tex
Exam 2h problem 3.

In order to manage class scheduling, the College decided that they
needed to create a new implementation of the \verb|Set| data
structure.  They went with the lowest bidder, which
turned out to be a bunch of BU students.  Now, having paid for this
code, the College needs to test it, and they turn to you.

Unfortunately, the code the BU students produced is so convoluted that
it doesn't bear looking at.  All you have to go on is that the
\verb|Set| data structure obeys the following interface:

\begin{verbatim}
;; A Set implements:
;; - insert : String -> Set
;;   adds given string to this set, if it isn't already there
;;   (otherwise produces this set)
;; - remove : String -> Set
;;   removes given string from this set, if it's already there
;;   (otherwise produces this set)
;; - size : -> Number
;;   count the elements of this set
;; - has? : String -> Boolean
;;   is the given String in this set?

;; empty-set is a Set value containing no elements
\end{verbatim}
\noindent
\verb|Set|s should satisfy the following property, called the
``insert-size'' property, for any element and
set:

\begin{quote}
If we insert any element into any set, then the resulting set is the
same size as the original set \emph{if} the element was already in the
set, and the resulting set is one larger than the original set
if the element was \emph{not} already in the set.
\end{quote}

\begin{enumerate}
\item Codify the ``insert-size'' property as a predicate.  Write a
  test case that should pass (if the sets work right) using the
  predicate you have defined.
\end{enumerate}

\newpage
\noindent
The College wants to be really sure that their sets are correct, and
they've come up with another property that they think is true, called
the ``insert-remove'' property:

\begin{quote}
If we insert element any element $a$ into any set, and then remove any
element $b$ from the resulting set, the result has the same size as if
we do the two operations in the reverse order, i.e., remove $b$, then
insert $a$.
\end{quote}

\noindent
The College is considering adding this to the test suite as well.

\begin{enumerate}
\setcounter{enumi}{1}

\item Codify this property as a predicate, and write a test case that
  should pass using the predicate.

\item Is the ``insert-remove'' property true for all sets?  If so,
  give an explanation.  If not, write a counter-example (i.e., a
  failing test case) using your predicate.

\begin{solution}
\begin{alltt}
\rubricpts{1 pt -- contract & purpose}
;; check-insert-size : Set String -> Boolean
;; check the "insert-size" property on s and i.
\rubricpts{4 pts -- code}
(define (check-insert-size s i)
  (= (s . insert i . size)
     (cond [(s . has? i) (add1 (s . size))]
           [else               (s . size)])))

\rubricpts{2 pts -- test case}
(check-expect (check-insert-size empty-set "hi") true)

\rubricpts{1 pt -- contract & purpose}
;; check-remove-insert : Set String -> Boolean
;; check the "remove-insert" property on s, a, and b.
\rubricpts{3 pts -- code}
(define (check-remove-insert s a b)
  (= (s . insert a . remove b . size)
     (s . remove b . insert a . size))

\rubricpts{1 pt -- successful test}
(check-expect (check-remove-insert empty-set "yes" "no") true)

;; Property does not hold.
;; Counter-example (failing test):
\rubricpts{3 pts -- failing test}
(check-expect (check-remove-insert empty-set "yes" "yes") true)
\end{alltt}
\end{solution}

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
\fi
\end{problem}

>>>>

In mathematics, an {\bf unordered} pair is a pair of values in which
the order of the elements does not matter.  So for example, if
$\{3,4\}$ is an unordered pair, then it should be considered ``the
same'' as the unordered pair $\{4,3\}$.  Here is an implementation of
{\tt UnPair}, which represents unordered pairs.  Notice that both {\tt
  equals} and {\tt hashCode} have been overridden.

\begin{verbatim}
class UnPair<X> {
  X left;
  X right;
  UnPair(X left, X right) {
    this.left = left;
    this.right = right;
  }

  // Compute the hash of this unordered pair.
  public int hashCode() {
    return left.hashCode();
  }

  // Is this unordered pair the same as the given unordered pair?
  public boolean same(UnPair<X> p) { ... }

  // Is this unordered pair the same as the given object?
  public boolean equals(Object that) {
    return (that instanceof UnPair)
        && this.same((UnPair<X>)that);
  }
}
\end{verbatim}

\newpage
\noindent
Part (A): Implement the omitted {\tt same} method that compares this
unordered pair to a given unordered pair.  This method should work
regardless of the order of the pair, so for example {\tt new
  UnPair<Integer>(3,4)} is the same (according to {\tt same}) as {\tt
  new UnPair<Integer>(4,3)}.

\newpage
\noindent
Part (B): Assuming {\tt same} and {\tt equals} work as expected, is
the given {\tt hashCode} method valid?  That is, does it satisfy or
violate the law of {\tt hashCode}?  If it is valid, give an argument
for \emph{why}.  If it is not, give a counter-example to the law of
{\tt hashCode}.
\end{problem}
\newpage
